---
output:
  md_document:
    variant: markdown_github
---

# Purpose

The aim of this folder it to contain information for the data science exam. It will provide detailed explanation of the actions that will be carried out in answering the questions in the assessment. The README will address the what, why and how questions. Specifically the motivation, the reason for building the project, the problems solved and what the projects taught us, amongst other important questions.  
The Questions will be answered in the three different folders to make it easier to separate objects and plots relating to each specific question. 

#Management of R projects
The first step taken was to create a folder including the project and inside the folder three folders were created using the preinstalled Texevier package for each question.

```{r eval=FALSE}
CHOSEN_LOCATION <- "C:/Users/gariz/DataScience/"
fmxdat::make_project(FilePath = glue::glue("{CHOSEN_LOCATION}Solution/"), 
                     ProjNam = "23338784")

Texevier::create_template(directory = glue::glue("{CHOSEN_LOCATION}Solution/23338784/"), template_name = "Question1")
Texevier::create_template(directory = glue::glue("{CHOSEN_LOCATION}Solution/23338784/"), template_name = "Question2")
Texevier::create_template(directory = glue::glue("{CHOSEN_LOCATION}Solution/23338784/"), template_name = "Question3")


```
After creating the new *R.project*, we move on to the next step of loading and installing the packages that will be used to answer the questions. This is done after cleaning the environment to make sure no cache memory will be used from previous projects. Then followed by loading the data for all the questions into the respective **data/** folder (data folder in each question). These steps will be carried out per each question answered.

# Question 1


Load in coding scripts

```{r}

rm(list = ls()) # Clean your environment:
gc() # garbage collection 
library(pacman)
p_load(tidyverse, rmsfuns, lubridate)

# Source in all your functions:
list.files('Question1/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

```


# Data loading

Loading in some really crucial data here, and then producing a beautiful plot:

```{r eval=FALSE}
knitr::opts_chunk$set(echo = False)

if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
list.files('..//Question1/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))


```

# Question 2
## Billionaires  

Just like the previous question this report will need to be reported in a less formal manner, hence this question will not require the use of Texevier. Thus, the output file will be knitted using the rmarkdown.  

First task will be to load the code and the data into the folders of Question 2. The data of billionaires will be uploaded into the */Question2/data.csv* file. This question will include figures that will be generated by ggplot package for FIN24.
```{r}

```

# Question 3

## Tweets

This question involves the use of the Texevier package and the extra necessary data manipulation to answer the question. The file for the Texevier was formed using the package and the evaluation will be completed in the pdf files.
```{r}

```


