---
title: "Question1"
output: pdf_document
---

```{r setup, eval=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = False)

if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
list.files('..//Question1/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
```

# Data Loading
```{r eval=FALSE}
pacman::p_load(tidyverse)
library(tidyverse)

movies <- read_csv("Question1/data/Movies.csv")


```

We first take a glimpse of the contents of the dataset using the glimpse(movies) function.
```{r eval=FALSE}
glimpse(movies)
```

The next step is to address her theories claim by claim using the movies dataset now included in the folder.  

The first claim made is that Rotten Tomatoes was a great platform and that audience would over rate a movies if it was above 85% in rating. We first have to make sure our data is tidy before we get into wrangling
```{r eval=FALSE}
movies %>%
  filter(`Audience  score %` > 80 & `Rotten Tomatoes %` > 80)

```

Next Claim : 
Disney films may not have the highest grossing numbers, but they've always been the most profitable of all the leading studios.
```{r eval=FALSE}
movies %>%
  group_by(`Lead Studio`, 'Profitability', `Worldwide Gross`) %>%
  summarise(top_profit = sum(Profitability)) %>%
  
  arrange(desc(Profitability, `Worldwide Gross`))



  
```

The next claims is that, Audiences are always drawn to the highest grossing lms. In fact, I bet the correlation
between the world wide grossing numbers and audience scores would be near 80%.
```{r}


```




## Including Plots

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
